\documentclass[10pt,stdletter,dateno]{newlfm}
%\usepackage{kpfonts}
\usepackage{url}

\widowpenalty=1000
\clubpenalty=1000

\newlfmP{headermarginskip=20pt}
\newlfmP{sigsize=50pt}
\newlfmP{dateskipafter=20pt}
\newlfmP{addrfromphone}
\newlfmP{addrfromemail}
\PhrPhone{Phone}
\PhrEmail{Email}

\namefrom{Timothy J. Schumacher, Ph.D.}
\addrfrom{%
    \today\\[10pt]
    Timothy J. Schumacher, Ph.D.\\
    P.O. Box 7413\\
    Boulder, CO USA 80306-7413
}
\phonefrom{+1 720-220-8656}
\emailfrom{schumact@gmail.com}
\addrto{% Who we are sending to:
    Senior Java Application Developer \\
    Reference Number: JS/PRAGUEJAVA/4815342 \\
    Prague \\
    Czech Republic
}

\greetto{To Whom It May Concern,}
\closeline{Sincerely,}

\begin{document}
\begin{newlfm}

I am writing to apply for the Senior Java Software Engineer position posted on webjobz.com, reference number ``JS/PRAGUEJAVA/4815342''.

During the past 6 years with my current employer, I acquired a broad skillset 
that makes me an ideal candidate for this position.  I am involved with every aspect of web application 
development with Java.  As the sole maintainer of a web application used in a piece of IT equipment, I am 
in charge of client-side development, server-side development, nightly builds and deployment 
of the application.  This role has forced me to become proficient with everything from JSP to Servlets to Javascript to CSS.  
In addition, I am familiar with the Java Native Interface, both calling C++ from Java and calling Java from C++.  I am familiar with 
several frameworks, including Apache Struts and Spring.  I am very familiar with Apache Tomcat, and also have some exposure to Glassfish.

In addition, I have expert knowledge in the area of implementing C/C++ server/daemon programs.  I have been intimately involved 
in the design and implementation of several such processes in a linux environment and as such have a deep understanding of the 
interprocess communication mechanisms in linux.  One example is an implementation of a SCSI endpoint for a storage device.  

Although I am currently residing in the U.S., I am looking to move to Europe as I have a family member there.  
Ideally, I would look for a 1 to 3 year agreement.  I have visited the Czech Republic and would love the opportunity 
to spend more time there.

Enclosed is my current resume.  Also, I maintain a personal server as a hobby that has 
other information about me at:

\url{http://timmy.TransientRants.com}

Please let me know if there are any other materials or information that will assist you in processing my application.

Thank you for your time and consideration.  I look forward to hearing from you.

\end{newlfm}
\end{document}

