
\resheading{Work Experience}
\begin{itemize}
\item
	\ressubheading{Qualstar Corporation}{Boulder, CO}{Software Engineer}{May 2006-Present}
	\begin{itemize}
		\resitem{Built and maintained several daemon processes to manage the \href{http://www.qualstar.com/business/data-storage/xls-enterprise/}{XLS Enterprise Tape Library}.}
		\resitem{Download/compile/integrate new versions of \href{http://gcc.gnu.org}{GCC} as they become available.}
		\resitem{Wrote several shared libraries and java native methods to access them from Java applications.}
		\resitem{Designed a C++ application with an embedded JVM to access Java functionality from a C++ program.}
        \resitem{Implemented the Automation/Drive Interface (ADI) between IBM drives and tape libraries.}
        \resitem{Implemented a SCSI protocol endpoint in a tape library.}
		\resitem{Maintained a build system, wrote several shell scripts to automate deployment of software packages.}
	\end{itemize}

\item 
    \ressubheading{University of Colorado at Denver}{Denver, CO}{Adjunct Faculty}{Fall 2011}
	\begin{itemize}
		\resitem{Taught Introduction to Statistics. (1 Section)}
	\end{itemize}

\item 
    \ressubheading{Colorado Mountain College}{Dillon, CO}{Adjunct Faculty}{2009 - 2011}
	\begin{itemize}
		\resitem{Survey of Calculus Instructor. (3 Sections)}
	\end{itemize}

\item 
	\ressubheading{University of Colorado}{Boulder, CO}{Graduate Instructor}{August 2001 - May 2008}
	\begin{itemize}
		\resitem{Taught several courses, including Calculus I,II and III.}
        \resitem{Maintained course websites and wrote java applets to illustrate mathematical concepts to students.}
		\resitem{Held regular office hours, staffed a walk in help lab, and wrote/proctored/graded exams.}
	\end{itemize}

\item
	\ressubheading{University of Colorado}{Boulder, CO}{Research Assistant}{Summer 2000}
	\begin{itemize}
		\resitem{Developed code in C++ to solve partial differential equations using the Finite Element Method.}
        \resitem{Wrote visualization tools using OpenGL.}
        \resitem{Implemented a Linear Algebra library in C++ to solve various linear systems.}
		\resitem{Set up a cluster with linux, used MPI to implement parallel processing code.}
	\end{itemize}
%\item
%	\ressubheading{University of Colorado}{Boulder, CO}{Informal Program Coordinator}{August 2003 - May 2004}
%	\begin{itemize}
%		\resitem{Managed \$10,000 budget for student programs in residence halls.}
%		\resitem{Coordinated informal student-faculty programs on campus.}
%		\resitem{Supervised a tutor training program for small group tutors.}
%	\end{itemize}
\end{itemize}
